Stable Neo-Hookean Flesh Simulation

### 2019-12-02 LaTeX-Master-Vorlage/chapter/Background.tex
cal cal cal

\begin{addmargin}[1cm]{1cm}
a: Scalar \\
\textbf{A}: Matrix or tensor \\
\textbf{a}: Vector \\
vec(\textbf{A}) = $\boldsymbol{\check{a}}$: Vectorized matrix \\
$\mathbb{A} = \boldsymbol{\check{A}}$: matrix-of-matrices
\end{addmargin}

@@

\todoredefined[inline]{
TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
}

@@

\[
\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
\]

@@

\[
F = R S
\]

>>>>

\begin{addmargin}[1cm]{1cm}
a: Scalar \\
\textbf{A}: Matrix or tensor \\
\textbf{a}: Vector \\
vec(\textbf{A}) = $\mathbf{\check{a}}$: Vectorized matrix \\
$\mathbb{A} = \mathbf{\check{A}}$: matrix-of-matrices
\end{addmargin}

@@

\todoredefined[inline]{
TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end. Add Frobenius norm?
}

@@

\begin{equation}\label{eq:deformation_gradient}
\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}.
\end{equation}

Using the SVD theorem mentioned in theorem \ref{SVD} $\mathbf{F}$ can be written in the form of

\begin{equation}\label{eq:svd_gradient}
\mathbf{F} = \mathbf{U \Sigma V\intercal}
\end{equation}

in which $\mathbf{\Sigma}$ stands for
\begin{equation}\label{eq:svd_simga}
\mathbf{\Sigma} = \left[\begin{matrix}  \sigma_0 & 0 & 0 \\ 0 & \sigma_1 & 0 \\ 0 & 0 & \sigma_2 \end{matrix}\right] .
\end{equation}

The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$. Unlike the normal convention the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} the rotation variant moves reflections to $\mathbf{\Sigma}$. This results into $\operatorname{det}(\mathbf{U})=\operatorname{det}(\mathbf{V})=1$ and the property that $\Sigma$ is allowed to have negative entries.

@@

\[
\mathbf{F} = \mathbf{RS}
\]

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
game over
cal cal cal

\subsection{The Energy Hessian Terms}
Calculations

\subsection{The Tikhonov, Mu, and Gradient Terms}
Calculations

@@

>>>>

\subsection{The Energy Hessian Terms}
Using the scalar notation for F the hessian of the energy can be written in a fourth-order matrix-of-matrices:
\[
\frac{\partial^2 \psi}{\partial F^2} = \frac{\partial P(F)}{\partial F} = 
\left[\begin{array}{ccc}{\left[\frac{\partial P(F)}{\partial f_0}\right]} & {\left[\frac{\partial P(F)}{\partial f_3}\right]} & {\left[\frac{\partial P(F)}{\partial f_6}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_1}\right]} & {\left[\frac{\partial P(F)}{\partial f_4}\right]} & {\left[\frac{\partial P(F)}{\partial f_7}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_2}\right]} & {\left[\frac{\partial P(F)}{\partial f_5}\right]} & {\left[\frac{\partial P(F)}{\partial f_8}\right]} \end{array}\right]
\]

in which each entry is defined as
\[
\frac{\partial P(F)}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F} \right]
\]
\[
\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial F}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{F \mu \frac{2}{\left(\operatorname{tr}(\mathrm{F}^{T}F) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
\]
\[
r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial F}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial F\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}
\]
Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following.

\subsection{The Tikhonov, Mu, and Gradient Terms}
\textbf{Tikhonov}: The Tikhonov term can be viewed as a fourth-order matrix-of-matrices
\[
\mathbb{T} = \frac{\partial \mathbf{F}}{\partial f_i} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
\]
If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbb{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F. It serves as a regularizer for the rest of the energy
\[
\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbb{I} = \in \mathbb{R}^{9x9}.
\]

\textbf{Mu}: The Mu term has the same structure with different entries
\[
\mathbb{M} = \mathbf{F} f_i = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
\]
When vectorizing $\mathbb{M}$ the resulting matrix has the squared values of $f_i$ placed on the diagonal
\[
\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}.
\]
This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$
\[
\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal.
\]
This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues one can calculate
\[
\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right)
\]
in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in eq. \ref{eq:svd_simga}. The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$. The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large strech.

\textbf{Gradient}:
\begin{align*}
\mathbb{G}(\mathbf{F}) &= \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi} \\ \\
\operatorname{vec}(\mathbb{G}(\mathbf{F})) &= \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\intercal = \mathbf{\check{g}} \mathbf{\check{g}}^\intercal
\end{align*}

@@

\todoredefined[inline]{
TODO: Make notation consistent (bold, cursive etc.) Explain better each step. Include all calculations? Make matrix of matrices more beautiful (more space). Eigenvalues of Mu term?
}
